### 2013-09-16 results.tex
added central axis mr:arfi fig
updated metrics on axis ratio over/underestimation
added relative diffs in central axis ratios
MR annotated anatomy included
latest raw axis plots

@@

@@

>>>>

Figure~\ref{fig:mr_anatomy} shows the anatomic zones, etc. in ARFI imaging, blah blah blah\ldots

\input{fig_mr_anatomy}

@@

Measurements of the prostate dimensions along the three standard anatomic axes
(apex-to-base, lateral-to-lateral, and anterior-to-posterior) were made
(Table~\ref{tab:mr_arfi_axes}), and the correlation between the imaging axis
measurements and pathology was performed (Figure~\ref{fig:mr_arfi_path_axes}).
To evaluate the relative shape of the prostate in each imaging modality, the
relative ratios of the axes in imaging and pathology for the total prostate
volume were compared (Figure~\ref{fig:mr_arfi_total_axes}), and the relative
ratios of the central gland / zone anatomy were compared for MR and ARFI
imaging (Figure~\ref{fig:mr_arfi_central_axes}).  The mean ratio differences
between ARFI imaging, T2WI MR and pathology are compiled in
Table~\ref{tab:axis_ratio_over_under}.

@@

\input{fig_mr_arfi_path_axes}

\input{fig_mr_arfi_total_axes}

\input{fig_mr_arfi_central_axes}

\input{tab_axis_ratio_over_under}
